### 2020-04-09 Thesis-Chapter2-Background.tex
Work on background

\begin{itemize}
    \item \acf{AWA} of 1789 \cite{congress_1789}
    \item Bill of Rights: Amendments I, IV, and V \cite{madison_1791}
    \item \acf{AECA} of 1976 established export controls over strong encryption techniques
        introduced ITAR (International Traffic in Arms Regulations) \cite{morgan_hr13680_1976} \cite{kehl_right_2015}
    \item \acf{FISA} of 1978 \cite{rodino_1978}
        (FISA has been the subject of frequent FBI abuse: \cite{shamsi_2011} \cite{tucker_2020})
        % (the FBI almost lost some provisions; follow up on https://apnews.com/110ff653e98478da66765897dde3d613,
        %     https://www.washingtontimes.com/news/2020/mar/15/adam-schiff-fisa-reform-intervention-protects-fbi-/,
        %     https://saraacarter.com/fisa-senate-passes-measure-extending-surveillance-powers-abuses-not-addressed/)
    \item \acf{CFAA} of 1986 \cite{hughes_hr4718_1986} \cite{wolff_computer_2016}
    \item \acf{ECPA} of 1986 \cite{kastenmeier_hr4952_1986}
    \item \acf{CALEA} of 1994 \cite{edwards_hr4922_1994}
    \item Uniting and Strengthening America by Providing Appropriate Tools Required to Intercept and Obstruct Terrorism
        (USA PATRIOT ACT) Act of 2001 \cite{sensenbrenner_2001}
    \item \acf{PAA} of 2007 \cite{mcconnell_s1927_2007}
    \item \acf{FISAAA} of 2008 \cite{reyes_hr6304_2008}
    \item Uniting and Strengthening America by Fulfilling Rights and Ensuring Effective Discipline Over Monitoring
        (USA FREEDOM) Act of 2015 \cite{sensenbrenner_2015}
    \item \dots
\end{itemize}

@@

\begin{itemize}
    \item The \ac{clipperchip} \cite{press_1993} \cite{thompson_2015}
    \item The SAFE Act \cite{goodlatte_hr3011_1996}
    \item Encrypted Communications Privacy Act (mix of SE protection and EA guidelines?) \cite{leahy_s376_1997}
    \item Encryption Protects the Rights of Individuals from Violation and Abuse in CYberspace (E-PRIVACY) Act
        (like above?) \cite{ashcroft_s2067_1998}
    \item Encryption for the National Interest Act and Tax Relief for Responsible Encryption Act (introduced by same rep
        on same day) \cite{goss_hr2616_1999} \cite{goss_hr2617_1999}
    \item Compliance with Court Orders Act of 2016 (discussion draft) \cite{burr_2016}
    \item The Secure Data Act (federal SE protections) \cite{lofgren_hr5823_2018}
    \item The ENCRYPT Act (state SE protections) \cite{lieu_hr4170_2019}
    \item The EARN IT Act \cite{graham_s3398_2020}
    \item \dots
\end{itemize}

@@

\begin{itemize}
    \item Australia: in 2018 passed its Assistance and Access bill \cite{ag_2018} \cite{newman_2018}
    \item UK: Investigatory Powers Act \cite{legislature_2016}
    \item EU: GDPR \cite{parliament_2016}
    \item China: \cite{donahue_comparative_2018}
    \item Israel: \cite{donahue_comparative_2018}
    \item Japan, Korea? -- can't find anything
    \item \dots General, see \cite{budish_encryption_2018}
\end{itemize}

@@

\begin{itemize}
    \item Clipper chip/third-party key escrow \cite{blaze_protocol_1994}
    \item Oblivious key escrow \cite{goos_oblivious_1996}
    \item Partial key escrow (see \cite{denning_taxonomy_1996})
\end{itemize}

@@

\begin{itemize}
    \item CLEAR \cite{ozzie_2018}
    \item Device escrow with HW \cite{savage_lawful_2018}
    \item Computational, blockchain approaches \cite{phan_key_2017}
    \item Lawful hacking \cite{nguyen_lawful_2017} \cite{soesanto_2018} \cite{kerr_encryption_2017}
    \item Forced password disclosure \cite{bittenbender_2019} \cite{kerr_encryption_2017}
    \item Alternative paths to plaintext (access device while unlocked; find copies elsewhere)
        \cite{kerr_encryption_2017}
\end{itemize}

>>>>

\newcommand{\lawstart}[0]{\begin{itemize}}
\newcommand{\law}[3]{\item #1: \textbf{#2} \cite{#3}} % Year, name, citation
\newcommand{\lawsend}{\end{itemize}}

\lawstart
    \law{1789}{\acf{AWA}}{congress_1789}
    \law{1791}{Bill of Rights: Amendments I, IV, and V}{madison_1791}
    \law{1976}{\acf{AECA}}{morgan_hr13680_1976}
% Established export controls over strong encryption techniques introduced ITAR (International Traffic in Arms
% Regulations) \cite{kehl_right_2015}
    \law{1978}{\acf{FISA}}{rodino_1978}
% (FISA has been the subject of frequent FBI abuse: \cite{shamsi_2011} \cite{tucker_2020})
% (the FBI almost lost some provisions; follow up on https://apnews.com/110ff653e98478da66765897dde3d613,
%     https://www.washingtontimes.com/news/2020/mar/15/adam-schiff-fisa-reform-intervention-protects-fbi-/,
%     https://saraacarter.com/fisa-senate-passes-measure-extending-surveillance-powers-abuses-not-addressed/)
    \law{1986}{\acf{CFAA}}{hughes_hr4718_1986}
% \cite{wolff_computer_2016}
    \law{1986}{\acf{ECPA}}{kastenmeier_hr4952_1986}
    \law{1994}{\acf{CALEA}}{edwards_hr4922_1994}
    \law{2001}{\acf{USAPATRIOT} Act}{sensenbrenner_2001}
    \law{2007}{\acf{PAA}}{mcconnell_s1927_2007}
    \law{2008}{\acf{FISAAA}}{reyes_hr6304_2008}
    \law{2015}{\acf{USAFREEDOM} Act}{sensenbrenner_2015}
\lawsend

@@

\lawstart
    \law{1993}{The \ac{clipperchip}}{press_1993}
% \cite{thompson_2015}
    \law{1996}{The SAFE Act}{goodlatte_hr3011_1996}
    \law{1997}{Encrypted Communications Privacy Act}{leahy_s376_1997}
% mix of SE protection and EA guidelines?
    \law{1998}{Encryption Protects the Rights of Individuals from Violation and Abuse in CYberspace (E-PRIVACY) Act}{ashcroft_s2067_1998}
% like above?
    \law{1999}{Encryption for the National Interest Act}{goss_hr2616_1999}
    \law{1999}{Tax Relief for Responsible Encryption Act}{goss_hr2617_1999}
% ^^ these two introduced by same rep on same day
    \law{2016}{Compliance with Court Orders Act (discussion draft)}{burr_2016}
    \law{2018}{The Secure Data Act}{lofgren_hr5823_2018}
% federal SE protections
    \law{2019}{The ENCRYPT Act}{lieu_hr4170_2019}
% state SE protections
    \law{2020}{The EARN IT Act}{graham_s3398_2020}
\lawsend

@@

\newcommand{\countrystart}[0]{\begin{itemize}}
\newcommand{\country}[1]{\item \textbf{#1:}} % Country
\newcommand{\countryend}{\end{itemize}}

\countrystart
    \country{Australia} In 2018 passed its Assistance and Access bill \cite{ag_2018} \cite{newman_2018}
    \country{UK} Investigatory Powers Act \cite{legislature_2016}
    \country{EU} GDPR \cite{parliament_2016}
    \country{China} See \cite{donahue_comparative_2018}
    \country{Israel} See \cite{donahue_comparative_2018}
    \country{Japan, Korea} can't find anything
    \country{General} See \cite{budish_encryption_2018}
\countryend

@@

\newcommand{\propstart}[0]{\begin{itemize}}
\newcommand{\prop}[2]{\item \textbf{#1} \cite{#2}} % Proposal name, citation
\newcommand{\propend}{\end{itemize}}

\propstart
    \prop{Clipper chip/third-party key escrow}{press_1993}
% toasted by \cite{blaze_protocol_1994}
    \prop{Oblivious key escrow}{goos_oblivious_1996}
    \prop{Partial key escrow}{denning_taxonomy_1996}
\propend

@@

\propstart
    \prop{CLEAR}{ozzie_2018}
    \prop{Device escrow with HW}{savage_lawful_2018}
    \prop{Computational, blockchain approaches}{phan_key_2017}
    \prop{Lawful hacking}{nguyen_lawful_2017}
% see also \cite{soesanto_2018} \cite{kerr_encryption_2017}
    \prop{Forced password disclosure}{kerr_encryption_2017}
% see also \cite{bittenbender_2019}
    \prop{Alternative paths to plaintext}{kerr_encryption_2017}
% access device while unlocked; find copies elsewhere
\propend

### 2020-04-09 Thesis-Glossary.tex
Work on background

% Start terms
\newterm{wicked-prob}{wicked problem}{
    A problem
}

@@

>>>>

% Start terms
\newterm{wicked-prob}{wicked problem}{
    A problem lacking clear formulations, causes, resolutions, or metrics. Consistenly difficult to solve, and often
    social or political in nature
}

@@

% Custom acronyms

\newabbreviation{USAPATRIOT}{USA PATRIOT}{Uniting and Strengthening America by Providing Appropriate Tools Required to Intercept and Obstruct Terrorism}
\newabbreviation{USAFREEDOM}{USA FREEDOM}{Uniting and Strengthening America by Fulfilling Rights and Ensuring Effective Discipline Over Monitoring}
